Joint modelling

### 2020-11-26 manuscript/jm.Rmd
Cleaning up, finishing touches on manuscript, work on supplement

```{r}
jm_hypothesis_res_list[["d_dimer_age_sex"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$d_dimer_increases_death,
    fit_d_dimer_age_sex,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex",
    model_check = "Suspicious")

@@

```{r}
jm_hypothesis_res_list[["d_dimer_age_sex_hcq"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$d_dimer_increases_death,
    fit_d_dimer_age_sex_hcq,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex, hcq",
    model_check = "Problematic")

@@

```
```{r}
jm_hypothesis_res_list[["IL_6_age_sex"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$IL_6_increases_death,
    fit_IL_6_age_sex,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex",
    model_check = "Suspicious")

@@

```{r}
jm_hypothesis_res_list[["IL_6_age_sex_hcq"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$IL_6_increases_death,
    fit_IL_6_age_sex_hcq,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex, hcq",
    model_check = "Suspicious")

>>>>

```{r}
jm_hypothesis_res_list[["d_dimer_age_sex"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$d_dimer_death,
    fit_d_dimer_age_sex,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex",
    model_check = "Suspicious")

@@

```{r}
jm_hypothesis_res_list[["d_dimer_age_sex_hcq"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$d_dimer_death,
    fit_d_dimer_age_sex_hcq,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex, hcq",
    model_check = "Problematic")

@@

```
```{r}
jm_hypothesis_res_list[["IL_6_age_sex"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$IL_6_death,
    fit_IL_6_age_sex,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex",
    model_check = "Suspicious")

@@

```{r}
jm_hypothesis_res_list[["IL_6_age_sex_hcq"]] <-
  bayesian_hypothesis_res_from_jm(
    hypotheses$IL_6_death,
    fit_IL_6_age_sex_hcq,
    coefficient_name = "Assoc|Long1|etavalue",
    adjusted  = "age, sex, hcq",
    model_check = "Suspicious")
